Location and Scale-Invariant Power Transformations for Transforming Data to

### 2025-10-28 manuscript_rmarkdown/manuscript.Rmd
Update discussion regarding ECN.

We introduced an empirical test for central normality to assess whether sequences
deviate from normality in a way that might require closer inspection prior to further processing.
The empirical test for central normality differs from other tests for normality, 
such as the Shapiro-Wilk test [@Shapiro1965-zd], as it assesses normality of the central portion
of a feature, instead of the entire feature. 
Compared to the central normality test and the Shapiro-Wilk test, the empirical central
normality test remains consistent in the presence of outliers, although the former
tests are more powerful when outliers are absent.

>>>>

We introduced an empirical test for central normality to assess whether sequences
deviate from normality in a way that might require closer inspection prior to further processing.
The empirical central normality test differs from other tests for normality, 
such as the Shapiro-Wilk test [@Shapiro1965-zd], as it assesses normality of the central portion
of a feature, instead of the entire feature. 
Compared to the Shapiro-Wilk test, the empirical central
normality test remains consistent when a feature was not sampled from a normal distribution,
such as a central normal distribution with $\kappa < 1.0$. This enables assessing
reasonable normality of (transformed) features in the presence of outliers.
